\section{Introduction}

\subsection{Background}

I am a computer scientist in training, with a background in software engineering and computer programming, focusing on data structures and algorithms. My interest in mathematics has always been present, but it was not until I began studying computer science that I realized the depth of my passion for the subject. I have always been fascinated by the intersection of mathematics and computer science, and I am constantly seeking ways to deepen my understanding of both fields. I believe that a strong foundation in mathematics is essential for any computer scientist, and I am committed to developing my mathematical skills to enhance my work in computer science.

\subsection{Experiences with Mathematical Learning}

My experiences with mathematical learning have been mostly positive, but I have encountered some challenges along the way. I have always been a strong student in mathematics, and I have consistently performed well in my math courses. I cared more about the enjoyment of solving problems than the grades. However, I have always struggled with mental math and have had to work hard to improve my skills in this area. I have also found that I learn best when I can see the practical applications of the mathematical concepts I am studying. I am a very hands-on learner, and I benefit greatly from working on real-world problems that require me to apply the mathematical concepts I have learned.

I know of trigonometry but have not studied it in depth. Furthermore, I lack a deep understanding of the trigonometric functions and their properties, and I have not yet explored the applications of trigonometry in computer science. The highest level of math I have completed is algebra 2, and I have not yet taken a calculus course. I am eager to learn more about trigonometry and calculus and to deepen my understanding of these mathematical fields.

\subsection{Goals for Mathematical Learning}

I have several goals for my mathematical learning. First and foremost, I want to develop a deep understanding of trigonometry and calculus and to be able to apply these concepts to real-world problems. I want to learn how to use trigonometry to model and solve problems in computer science, such as graphics and animation. I also want to learn how to use calculus to model and solve problems in computer science, such as optimization and machine learning. Additionally, I want to improve my mental math skills and my ability to work with mathematical concepts quickly and accurately. I believe that achieving these goals will enhance my work in computer science and enable me to tackle more complex and challenging problems in the field.

\subsection{Questions About Trigonometry and Calculus}

Before learning trigonometry and calculus, I have several questions about these mathematical fields. For trigonometry, I am curious about why radians are used sometimes instead of degrees, and I want to know what the practical applications of trigonometry are in computer science. For calculus, I am curious about what limits are and why they are important, and I want to know how to find the instantaneous rate of change of a function. I am also interested in learning about the different types of calculus, such as differential calculus and integral calculus. I hope to explore these questions and gain a deeper understanding of trigonometry and calculus as I continue my mathematical learning journey.

\subsection{Plan for Learning Trigonometry and Calculus}

To achieve my goals for mathematical learning, I have developed a plan to study trigonometry and calculus. I will begin by reviewing the basic concepts of trigonometry, such as the trigonometric functions and their properties. I will then move on to more advanced topics, such as trigonometric identities and equations. Most importantly, I will learn how to apply trigonometry to real-world problems in computer science. After completing my study of trigonometry, I will begin studying calculus. I will start with the basic concepts of calculus, such as limits and derivatives, and then move on to more advanced topics, such as integrals and differential equations. I will also learn how to apply calculus to real-world problems in computer science. By following this plan, I hope to deepen my understanding of trigonometry and calculus and to achieve my goals for mathematical learning.